The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-09-25 article.tex
No code example
Added missing figure number

  Many of the rendering options are available as parameters in the core API
  and as methods on the DepictionGenerator class. This includes substructure
  coloring, exemplified with this example reaction (see Figure~FIXME\ref{fig:depiction}):

\begin{verbatim}
TODO
\end{verbatim}

@@

The API has hardly changed, but the internals have significantly. Besides
the aforementioned overlap resolution, the engine also handles large ring
systems much better,
and handles stereochemistry of the input. Previously, double bond stereochemistry
was supported, but the new engine more efficiently uses this when creating 2D
layouts. Furthermore, the engine assigns wedge bond information based on
tetrahedral stereochemistry. These features are exemplified by the following
code and the resulting layout depiction in Figure~\ref{fig:sdgstereo}.

>>>>

  Many of the rendering options are available as parameters in the core API
  and as methods on the DepictionGenerator class. This includes substructure
  coloring, exemplified with an example reaction shown in Figure~4\ref{fig:depiction}.

@@

The API has hardly changed, but the internals have significantly. Besides
the aforementioned overlap resolution, the engine also handles large ring
systems much better,
and handles stereochemistry of the input. Previously, double bond stereochemistry
was supported, but the new engine more efficiently uses this when creating 2D
layouts. Furthermore, the engine assigns wedge bond information based on
tetrahedral stereochemistry. These features are exemplified by the following
code and the resulting layout depiction in Figure~6\ref{fig:sdgstereo}.
